```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

# Links {#links}

The `ft_links` function makes it easy to get URLs for full text versions of articles. You can for instance only use `fulltext` to pass DOIs directly to `ft_links` to get URLs to use elsewhere in your research workflow. Or you may want to search first with `ft_search`, then pass that output directly to `ft_links`. 

## Usage {#links-usage}

```{r}
library(fulltext)
```

List backends available

```{r}
ft_links_ls()
```

You can pass DOIs directly to `ft_links`

```{r}
res <- ft_links('10.3389/fphar.2014.00109')
res
```

The output is an S3 object, essentially a list. If you don't specify a `from` value, we try to guess the publisher and the named list in the output will match the publisher of the DOI. Here, that's Frontiers In, lowercased and as one word:


```{r}
res$frontiersin
```

The output is a named list with number of links found, the id (aka DOI), and in the `$data` slot is the links, which can include links for pdf, xml, plain (for plain text), unspecified and possibly others (publishers do lots of weird things).



Instead of passing DOIs directly, you can use `ft_search(()` to search first:

```{r}
(res1 <- ft_search(query='ecology', from='entrez'))
```

Then pass the output of that directly to `ft_links`

```{r}
(out <- ft_links(res1))
```

Here, the output name on the list matches the source passed in to `ft_links` from `ft_search`. 

```{r}
names(out)
```

You can alternatively pass in DOIs directly and specify the data source. Options include "plos", "bmc", "crossref", and "entrez". 

```{r}
x <- c("10.1371/journal.pone.0017342", "10.1371/journal.pone.0091497")
z <- ft_links(x, from = "plos")
z$plos$data
```

Fetch just the pdf links

```{r}
unname(vapply(z$plos$data, "[[", "", "pdf"))
```

## Links options {#links-options}

All data sources for `ft_links()` SHOULD accept configuration options BUT that does not work right now. Fix coming, see <https://github.com/ropensci/fulltext/issues/223>

As all functions in `fulltext`, you can pass on curl options to each function call or set them globally for the session, see the [curl options chapter](#curl-options).
