--- 
title: "fulltext manual"
date: "`r paste0('built on ', Sys.Date(), ' - for fulltext v', packageVersion('fulltext'))`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: ropensci-books/fulltext
description: "fulltext manual"
---

# fulltext manual

An R package to search across and get full text for journal articles

The `fulltext` package makes it easy to do text-mining by supporting the following steps:

* Search for articles
* Fetch articles
* Get links for full text articles (xml, pdf)
* Extract text from articles / convert formats
* Collect bits of articles that you actually need
* Download supplementary materials from papers

## Info

* Code: <https://github.com/ropensci/fulltext/>
* Package Documentation: <https://docs.ropensci.org/fulltext>
* Issues/Bug reports: <https://github.com/ropensci/fulltext/issues>
* CRAN: <https://cran.rstudio.com/web/packages/fulltext/>

## Citing fulltext

> Scott Chamberlain (2019). fulltext: Full Text of 'Scholarly' Articles Across
> Many Data Sources. R package version `r packageVersion("fulltext")`. https://docs.ropensci.org/fulltext (website)
> https://github.com/ropensci/fulltext/ (devel)
> https://books.ropensci.org/fulltext/ (user manual) 

## Installation

Stable version from CRAN

```{r eval=FALSE}
install.packages("fulltext")
```

Development version from GitHub

```{r eval=FALSE}
remotes::install_github("ropensci/fulltext")
```

Load library

```{r}
library('fulltext')
```
